Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Fluid Flows

### 2015-12-21 main.tex
Changed title

\title{An Investigation into the Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Fluid Flows}
%\title{A Comparison of Lattice Boltzmann Method Collision Operators for Accuracy, Stability and Efficiency in Simulating Non-Newtonian Flows}

@@

There are a number of non-Newtonian flows in engineering applications.
Cement slurries and concretes are best modeled as non-Newtonian fluids because they typically have a non-linear relationship between strain rate and shear stress.
In particular, cement slurries and concretes can be categorized as yield stress fluids. 
Yield stress fluids do not flow until a threshold value of stress, referred to as its yield stress, is exceeded.
Understanding the flow of cement slurries and concretes is important because they are used in the cementing of oil and gas wellbores, in construction, and blah blah blah.
If the cement job for an oil and gas wellbore is not completed successfully then gases and fluids can leak through the wellbore to contaminate ground water or the atmosphere ~\cite{grasinger2015simulation}.
The goal of understanding cement slurry and concrete flows during construction is to understand how construction forms can be completely filled as voids can lead to structural deficiencies ~\cite{RARR}.
Yield stress flow is relevant in many other disciplines and applications because of the many substances that can be modeled as Bingham plastics, e.g. pastes, paints, muds, molten plastics and metals, and blood \cite{wang2011lattice}. %MG: citation is for blood as non-Newtonian
Non-Newtonian flow is therefor relevant in the engineering and development of pastes and paints, flow and deformation of mud and clay in geotechnical engineering, understanding blood circulation in biomedical applications, materials science and manufacturing of metal and plastic parts, and in particular, the molding and casting of molten metals and plastics.

>>>>

\title{Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Fluid Flows}
%\title{A Comparison of Lattice Boltzmann Method Collision Operators for Accuracy, Stability and Efficiency in Simulating Non-Newtonian Flows}

@@

There are a number of non-Newtonian flows in scientific and engineering applications.
Cement slurries and concretes are best modeled as non-Newtonian fluids because they exhibit a non-linear relationship between strain rate and shear stress.
In particular, cement slurries and concretes can be categorized as yield stress fluids. 
Yield stress fluids do not flow until a threshold value of stress, referred to as its yield stress, is exceeded.
Understanding the flow of cement slurries and concretes is important because they are used in the cementing of oil and gas wellbores, in construction, and blah blah blah.
If the cement job for an oil and gas wellbore is not completed successfully then gases and fluids can leak through the wellbore to contaminate ground water or the atmosphere ~\cite{grasinger2015simulation}.
The goal of understanding cement slurry and concrete flows during construction is to understand how construction forms can be completely filled as voids can lead to structural deficiencies ~\cite{RARR}.
Yield stress flow is relevant in many other disciplines and applications because of the many substances that can be modeled as Bingham plastics, e.g. pastes, paints, muds, molten plastics and metals, and blood \cite{wang2011lattice}. %MG: citation is for blood as non-Newtonian
Non-Newtonian flow is therefor relevant in the engineering and development of pastes and paints, flow and deformation of mud and clay in geotechnical engineering, understanding blood circulation in biomedical applications, materials science and manufacturing of metal and plastic parts, and in particular, the molding and casting of molten metals and plastics.
